
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Let's build some networks we'll make use of here.
First, using the bibliometrix package.
```{r slices}
library(bibliometrix)
load("data/social_capital.rdata")

# Citation
fullcites <- histNetwork(df, min.citations = 1, sep = ";")
artcites <- histNetwork(df_art, min.citations = 1, sep = ";")

# Co-citation
art_co <- biblioNetwork(df_art, analysis="co-citation", network="references", sep=";", shortlabel = F)
full_co <- biblioNetwork(df, analysis="co-citation", network="references", sep=";", shortlabel = F)

# Converting to igraph objects
library(igraph)
art_citation<- graph_from_adjacency_matrix(artcites$NetMatrix, mode="directed", diag=F)
all_citation <- graph_from_adjacency_matrix(fullcites$NetMatrix, mode="directed", diag=F)

art_cocite <- graph_from_adjacency_matrix(art_co, mode="undirected", diag=F, weighted=T)
all_cocite <- graph_from_adjacency_matrix(full_co, mode="undirected", diag=F, weighted=T)

# Creating and index for matching later.
save(fullcites, artcites, art_citation, all_citation, art_cocite, all_cocite, file="data/bibmx_networks.Rdata")
```

Now, let's take those and generate some bibliographic coupling networks, using some old scripts of my own.
  NOTE: These are SLOW!
I'm including these because they're constructed slightly differently than the bibliometrix versions.
The above versions do not retain those cited that weren't in the original corpus (which matters especially for my uses of the citation network here). 

```{r bibcoupling}
source("scripts/Scientometric_Networks.R")
# I actually ran these individually & manually, but these work.
citation <- SciNets(df, "citation", c("ARTICLE", "LETTER", "NOTE", "REVIEW", "ARTICLE; EARLY ACCESS", "ARTICLE; BOOK CHAPTER"))
bibcoup <- SciNets(df, "bibcoup", c("ARTICLE", "LETTER", "NOTE", "REVIEW", "ARTICLE; EARLY ACCESS", "ARTICLE; BOOK CHAPTER"))
cocite <- SciNets(df, "cocite", c("ARTICLE", "LETTER", "NOTE", "REVIEW", "ARTICLE; EARLY ACCESS", "ARTICLE; BOOK CHAPTER"))
save(citation, bibcoup, cocite, file="data/networks.Rdata")
```
